---
title: "Errata for Peyton, Huber and Coppock (2022)"
subtitle: "The Generalizability of Online Experiments Conducted During the COVID-19 Pandemic"
format:
  pdf:
    output-file: peyton_huber_coppock_2022_errata.pdf
    toc: false
    number-sections: false
    geometry: margin=1in
    fontsize: 11pt
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(here)
library(tidyverse)
here::i_am("errata.qmd")

out <- function(f) read_csv(here::here("maintained", "output", f), show_col_types = FALSE)

figure_2 <- out("figure_2_noncojoint_correspondence.csv")
figure_3 <- out("figure_3_conjoint_correspondence.csv")
appendix_estimates <- out("appendix_study_estimates.csv")
appendix_cells <- out("appendix_table_cells.csv")
correspondence <- out("text_correspondence_summary.csv")
device <- out("text_device_metadata.csv")

corr <- function(name) correspondence$value[correspondence$quantity == name]
dev_value <- function(name) device$value[device$quantity == name]

pp <- function(x) sprintf("%.1f", x)
pct <- function(x) sprintf("%.0f", x)

# Spelled-out numbers have to be computed too, so the count in a corrected sentence is
# rendered rather than typed.
as_word <- function(n) {
  words <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten",
             "eleven", "twelve", "thirteen", "fourteen", "fifteen", "sixteen", "seventeen",
             "eighteen", "nineteen", "twenty")
  words[n]
}

# Each entry's location is stored as the sentence-internal phrase; a heading raises its
# first letter.
capitalize <- function(x) paste0(str_to_upper(str_sub(x, 1, 1)), str_sub(x, 2))

ae <- appendix_estimates |>
  mutate(study_base = str_replace(study_group, "^Press et al\\. \\(2013\\).*",
                                  "Press et al. (2013)"))

psv <- ae |> filter(str_detect(study_group, "prospective"),
                    estimate_type == "Unstandardized", survey == "Press et al. (2013)")
psv_cell <- function(term_name, outcome_name) {
  psv$estimate[psv$term == term_name & psv$outcome_group == outcome_name]
}

porter <- figure_2 |> filter(str_detect(study_group, "Porter"))
porter_significant <- porter |> filter(p_diff < 0.05)
story_label <- c("Podesta" = "John Podesta", "Sex trafficking" = "Trump",
                 "Scaramucci" = "Scaramucci", "Russian hackers" = "Vermont",
                 "D.C. Pizzagate" = "Pizzagate", "Obama Birtherism" = "Obama")
porter_names <- unname(story_label[porter_significant$study_group_detail])
porter_names <- porter_names[order(match(porter_names,
                                         c("John Podesta", "Trump", "Scaramucci", "Vermont")))]

russians <- figure_2 |> filter(study_group_detail == "Russian reporters")

conjoint <- ae |> filter(study_base == "Hainmueller & Hopkins (2015)")

knobe <- ae |> filter(study_base == "Knobe (2003)", estimate_type == "Unstandardized")
kn_direct <- knobe |> filter(knobe_Z_type == "Original", study == "Replication")
kn_covid <- knobe |> filter(knobe_Z_type == "Modified")
kn_se <- sqrt(kn_direct$std.error ^ 2 + kn_covid$std.error ^ 2)

larger_pair <- figure_2 |> filter(abs(estimate_ycls) >= abs(estimate_pre))

psv_terms <- unique(ae$term[str_detect(coalesce(ae$term, ""), "^90/")])
conventional_9070 <- as.numeric(str_extract(psv_terms[psv_terms == "90/70"], "\\d+$"))
```

```{r entries}
# THE ERRATA SPINE. Every correction is defined once, here, and the document below is
# rendered from it. The same rows are written out as errata_entries.csv at the foot of
# this file, so any other document that needs to state what was corrected reads them
# rather than keeping a second hand-typed copy that can quietly drift.
#
# [[...]] marks the span that changes, and is the only markup a published or corrected
# field may carry. Each renderer resolves it its own way: bold here, a \was{} macro in a
# future edition. Everything else in a field is literal text.
#
# Numbering is APPEND-ONLY. An entry number can already have been cited, so a later
# finding is added at the end and entries are never reordered, renumbered, merged or
# split.
#
# Corrected values are computed at render time, never typed: a field that carries a
# pipeline quantity is a str_glue() over the objects read in the setup chunk above.
# `location` holds the phrase the heading embeds, lowercased at its first letter so the
# heading can raise it; `form` is a future edition's choice of macro, "full" where the
# quoted passage is a whole sentence set as a block and "brief" where it is a fragment
# standing in for a single token.
#
# `claim_ids` names the ground truth rows the entry corrects, semicolon separated, and it is
# what makes "has this finding been published?" a query over the corpus rather than a reading
# of every note. It is empty where the entry has no ground truth row: a reference list is not
# an extraction claim. Every id listed here is checked against the ground truth by
# ground_truth/build_ground_truth.R, which refuses to finish on a dangling one.
entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note, ~claim_ids,

  1, "quantity", "pipeline", "full",
  "the four estimates attributed to the original study are the pre-COVID replication's",
  "online appendix, Section A.8, page 18",
  "In the original study, the 90/70 condition caused an increase in the proportion of subject that preferred the nuclear option by about [[37]] percentage points relative to the 90/90 condition. The estimated effect of the 90/45 condition, relative to the 90/90 condition, was [[51]] percentage points. Similarly, the 90/70 condition caused an increase in the proportion of subjects that approved of the nuclear option by about [[17]] percentage points, and the 90/45 condition caused an increase of about [[27]] percentage points.",
  str_glue(
    "In the original study, the 90/70 condition caused an increase in the proportion of ",
    "subject that preferred the nuclear option by about ",
    "[[{pp(100 * psv_cell('90/70', 'Prefer Nuclear Use'))}]] percentage points relative to ",
    "the 90/90 condition. The estimated effect of the 90/45 condition, relative to the ",
    "90/90 condition, was [[{pp(100 * psv_cell('90/45', 'Prefer Nuclear Use'))}]] percentage ",
    "points. Similarly, the 90/70 condition caused an increase in the proportion of subjects ",
    "that approved of the nuclear option by about ",
    "[[{pp(100 * psv_cell('90/70', 'Approve Nuclear Use'))}]] percentage points, and the ",
    "90/45 condition caused an increase of about ",
    "[[{pp(100 * psv_cell('90/45', 'Approve Nuclear Use'))}]] percentage points."),
  paste(
    "All four published figures are the estimates from the Aronow, Baron and Pinson (2019)",
    "pre-COVID replication rather than from Press, Sagan and Valentino (2013). The",
    "appendix's own Table 2 prints both columns and gives the original study 0.30, 0.48,",
    "0.05 and 0.28 against the replication's 0.37, 0.51, 0.17 and 0.27."),
  "a8_original_9070_prefer;a8_original_9045_prefer;a8_original_9070_approve;a8_original_9045_approve",

  2, "quantity", "pipeline", "full",
  "the count of significant differences",
  "online appendix, Section A.10, footnote 5, page 25",
  "Although all 6 replication estimates are smaller in magnitude than those in the original study, only [[two]] of these differences ([[John Podesta and Trump]] stories) are statistically distinguishable from zero.",
  str_glue(
    "Although all 6 replication estimates are smaller in magnitude than those in the ",
    "original study, only [[{as_word(nrow(porter_significant))}]] of these differences ",
    "([[{paste(paste(head(porter_names, -1), collapse = ', '), 'and', tail(porter_names, 1))}]] ",
    "stories) are statistically distinguishable from zero."),
  paste(
    "The two additional differences are significant at conventional levels before any",
    "adjustment for multiple comparisons, which is what the footnote describes; three of the",
    "four survive a Benjamini-Hochberg adjustment across the six stories. The 2023",
    "corrigendum corrected the same class of error in the article's Figures 2 and 3 and did",
    "not reach this footnote."),
  "a10_footnote_5_significant;a10_footnote_5_named",

  3, "quantity", "pipeline", "full",
  "the replication estimate and its distance from the benchmark",
  "online appendix, Section A.1, page 1",
  "Pooling across the pre-COVID studies, the summary effect size estimate is a 30 percentage point increase in support for Russian journalists. Our effect estimate of [[25.5]] points is 83% of this magnitude, and this difference of [[5.5]] percentage points is not statistically significant (P = 0.16).",
  str_glue(
    "Pooling across the pre-COVID studies, the summary effect size estimate is a ",
    "{pp(100 * russians$estimate_pre)} percentage point increase in support for Russian ",
    "journalists. Our effect estimate of [[{pp(100 * russians$estimate_ycls)}]] points is ",
    "{pct(100 * russians$estimate_ycls / russians$estimate_pre)}% of this magnitude, and this ",
    "difference of [[{pp(-100 * russians$estimate_diff)}]] percentage points is not ",
    "statistically significant (P = {sprintf('%.2f', russians$p_diff)})."),
  paste(
    "The sentence's own three figures do not agree with each other: 30 less 25.5 is 4.5, not",
    "5.5. The ratio and the p-value it also prints are both right, and both follow from the",
    "corrected estimate and difference."),
  "a1_replication_estimate;a1_difference",

  4, "quantity", "pipeline", "full",
  "the non-conjoint correspondence",
  "page 6",
  "The 24 of 28 correctly signed estimates from the other replications were, on average, [[49%]] as large as the pre-COVID summary effect sizes.",
  str_glue(
    "The 24 of 28 correctly signed estimates from the other replications were, on average, ",
    "[[{pct(100 * corr('avg_pct_precovid_nonconjoint'))}%]] as large as the pre-COVID summary ",
    "effect sizes."),
  str_glue(
    "The mean ratio over those 24 pairs is ",
    "{sprintf('%.3f', corr('avg_pct_precovid_nonconjoint'))}. The overall 73% and the conjoint ",
    "87% stated in the same paragraph both reproduce exactly, and the three are consistent ",
    "with one another only at {pct(100 * corr('avg_pct_precovid_nonconjoint'))} per cent."),
  "results_correspondence_nonconjoint",

  5, "quantity", "pipeline", "full",
  "the average duration among browser respondents",
  "page 10",
  "Those from web applications spent approximately 7 min less time completing surveys than those from web browsers, who spent an average of [[21.5]] min.",
  str_glue(
    "Those from web applications spent approximately ",
    "{pp(dev_value('duration_mean_browser') - dev_value('duration_mean_webapp'))} min less ",
    "time completing surveys than those from web browsers, who spent an average of ",
    "[[{pp(dev_value('duration_mean_browser'))}]] min."),
  str_glue(
    "{pp(dev_value('duration_mean_nonmobile'))} minutes is the average among nonmobile ",
    "respondents, which the next sentence uses."),
  "device_duration_browser",

  6, "quantity", "pipeline", "full",
  "the inattentive share",
  "page 11",
  "If 73% of respondents were attentive and [[26%]] inattentive, our replication estimate would, on average, match our pre-COVID benchmarks.",
  str_glue(
    "If {pct(100 * corr('avg_pct_precovid_overall'))}% of respondents were attentive and ",
    "[[{pct(100 * (1 - corr('avg_pct_precovid_overall')))}%]] inattentive, our replication ",
    "estimate would, on average, match our pre-COVID benchmarks."),
  str_glue(
    "The correspondence is {sprintf('%.1f', 100 * corr('avg_pct_precovid_overall'))} per ",
    "cent, so the two shares are the attentive figure and its complement."),
  "inattention_inattentive_share",

  7, "quantity", "pipeline", "full",
  "the number of estimated AMCEs",
  "online appendix, Section A.9, page 22",
  "In total, there are [[81]] estimated AMCEs in Figure A.10 – 41 for the original study and 41 for the replication.",
  str_glue(
    "In total, there are [[{nrow(conjoint)}]] estimated AMCEs in Figure A.10 -- ",
    "{sum(conjoint$study == 'Pre-COVID')} for the original study and ",
    "{sum(conjoint$study == 'Replication')} for the replication."),
  str_glue("The two component counts are right and Figure A.10 plots {nrow(conjoint)} points."),
  "a9_total_amces",

  8, "quantity", "pipeline", "brief",
  "the 90/70 condition's success rate",
  "online appendix, Section A.8, page 17",
  "2) a \"90/70\" condition in which the conventional strike had a [[75%]] chance of success",
  str_glue(
    "2) a \"90/70\" condition in which the conventional strike had a ",
    "[[{conventional_9070}%]] chance of success"),
  paste(
    "The condition's two siblings are described at the rates their labels name, a 90% chance",
    "for the 90/90 condition and 45% for the 90/45 condition, and the label is written 90/70",
    "in the same paragraph, in the sentence that follows it and on Figure A.8."),
  "a8_9070_success",

  9, "cross_reference", "pipeline", "full",
  "a reference to a table that does not exist",
  "online appendix, Section A.5, page 11",
  "[[Table A.5]] provides a summary of differences between the original study and the replications by treatment arm.",
  "[[Table 1]] provides a summary of differences between the original study and the replications by treatment arm.",
  paste(
    "The appendix carries no Table A.5. The table this sentence points at is captioned Table",
    "1 and appears on the following page; the deposited file that builds it is named",
    "`appendix_table_a5.tex`, so it is the printed caption rather than the reference that",
    "departed from the intended numbering."),
  "a5_table_reference",

  10, "definition", "pipeline", "full",
  "whether every replication estimate was smaller",
  "page 6",
  "[[All]] replication summary estimates were smaller in magnitude than their pre-COVID estimates, with 24 of 28 signed in the same direction.",
  "[[All but one of the]] replication summary estimates were smaller in magnitude than their pre-COVID estimates, with 24 of 28 signed in the same direction.",
  str_glue(
    "The exception is the support-for-redistribution pair, whose pre-COVID summary effect is ",
    "{sprintf('%.5f', larger_pair$estimate_pre)} and whose COVID-era estimate is ",
    "{sprintf('%.3f', larger_pair$estimate_ycls)}. It is one of the four pairs signed against ",
    "their benchmark, so the count in the second half of the sentence is unaffected."),
  "results_all_smaller_nonconjoint",

  11, "quantity", "pipeline", "full",
  "the standard error of the difference between the two intentionality arms",
  "online appendix, Section A.7, page 15",
  "The estimated treatment effect for the COVID-specific replication is about 0.01 points smaller than the direct replication (SE = [[0.04]], P = 0.46).",
  str_glue(
    "The estimated treatment effect for the COVID-specific replication is about ",
    "{sprintf('%.2f', kn_direct$estimate - kn_covid$estimate)} points smaller than the direct ",
    "replication (SE = [[{sprintf('%.2f', kn_se)}]], P = 0.46)."),
  paste(
    "0.04 is the standard error of the difference against the pre-COVID benchmark, given in",
    "the sentence that follows. The published P = 0.46 is the one-tailed p-value at the",
    "corrected standard error, so the sentence is internally consistent once the standard",
    "error is corrected."),
  "a7_covid_vs_direct_se"
) |>
  mutate(across(c(title, published, corrected, note, claim_ids), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# The spine's markup, resolved for this document.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")
```

`r capitalize(as_word(nrow(entries)))` corrections to the article and its online appendix, none of which changes a conclusion. Every corrected value below is computed at render time from the maintained reanalysis of the deposited replication archive, `10.7910/DVN/38UTBF`. The article is `10.1017/XPS.2021.17`; a corrigendum published in 2023, `10.1017/XPS.2022.23`, corrects the significance counts in the article's Figures 2 and 3 and the first paragraph of page 6, and nothing below repeats a correction that corrigendum already made. The reanalysis is at `active-maintenance-aec/peyton_huber_coppock_2022`.

Values on the percentage-point scale are stated to one decimal place throughout, including numbers that were not wrong. Bold marks the tokens that changed.

---

```{r emit-entries, results="asis"}
# A heading is only a heading when a blank line precedes it, so every entry opens with one.
walk(seq_len(nrow(entries)), function(i) {
  e <- entries[i, ]
  cat("\n\n## ", e$entry, ". ", capitalize(e$location), ": ", e$title,
      "\n\nPublished:\n\n> ", bold(e$published),
      "\n\nCorrected:\n\n> ", bold(e$corrected),
      "\n\n", e$note, "\n", sep = "")
})
```

```{r emit-spine}
# The machine-readable spine, written wherever this document is rendered, so that any
# other document stating what was corrected reads these rows rather than retyping them.
write_csv(entries, here("errata_entries.csv"))
```
